Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings

### 2021-02-03 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Worked on scheme color, fonts, and bibliography

\documentclass[hideothersubsections, usenames,dvipsnames,10pt]{beamer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsmath}
\usepackage{mathpazo}
\usepackage{hyperref}
\usepackage{multimedia}
\usepackage{multicol}
\usepackage{epsfig}
\usepackage{curves}
\usepackage{epsfig}
\usepackage{epic}
\usepackage{curves}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{multicol}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{fix-cm}
\usepackage{graphicx}
\usepackage{hyperref}

@@

% Color scheme
\definecolor{cerulean}{rgb}{0.16, 0.32, 0.75}
\definecolor{bdf}{rgb}{0.19, 0.55, 0.91}
\definecolor{offwhite}{RGB}{255,253,238}
\definecolor{red}{RGB}{213,94,0}
%#09BADB #DB1A71

\usetheme[right]{Berkeley}
\setbeamercolor{background canvas}{bg=offwhite}
\setbeamercolor{palette primary}{bg=cerulean,fg=white}
\setbeamercolor{palette secondary}{bg=bdf,fg=white}
\setbeamercolor{frametitle}{fg=offwhite}
%\setbeamercolor{sidebar}{bg=cerulean}

%\newenvironment{transitionframe}{\setbeamercolor{background canvas}{bg=bdf}\begin{frame}}{\end{frame}}
%\setbeamercolor{title}{fg=black}
%\setbeamercolor{itemize item}{fg=blue}
%\setbeamercolor{itemize subitem}{fg=blue}
%\setbeamercolor{enumerate item}{fg=blue}
%\setbeamercolor{enumerate subitem}{fg=blue}
%\setbeamercolor{button}{bg=offwhite,fg=blue}

\setbeamerfont{section in sidebar}{size=\fontsize{5.3}{5}\selectfont}
\setbeamerfont{subsection in sidebar}{size=\fontsize{4.4}{5.5}\selectfont}
%\setbeamerfont{subsubsection in sidebar}{size=\fontsize{4}{7}\selectfont}

@@

@@

\begin{frame}
\frametitle{?}
	\begin{itemize_3pt}
	\item Bloom and van Reenen (2010, 2019): Business practices, motivation
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Heterogeneity in Business Practices}
	\begin{itemize_3pt}
	\item Bloom and van Reenen (2010): Heterogeneity
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{}
	\begin{itemize_3pt}
	\item Bloom and van Reenen (2019): Correlation with productivity
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Business Practices of Small Firms}
	\begin{itemize_3pt}
	\item McKenzie and Woodruff (2009, 2017): Heterogeneity and predictiveness
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Business Practices of Small Firms}
	\begin{itemize_3pt}
	\item McKenzie and Woodruff (2009, 2017): Example categories and practices
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Best Practices for Small Firms}
	\begin{itemize_3pt}
	\item McKenzie and Woodruff (2017): Portable best practices
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{History and Prevalence}
	\begin{itemize_3pt}
		\item At least \textcolor{bdf}{USD 1 billion per year} (to 4-5 million beneficiary entrepreneurs; McKenzie, 2020)
		\item Classical training programs \emph{precede} evidence that business practices vary and are predictive for productivity
		\vspace{0.1in}
		\item Examples:
		\begin{itemize_3pt}
			\item Start and Improve Your Business (ILO)
			\item Business Edge (IFC)
			\item EMPRETEC Entrepreneurship Training Workshop (UNCTAD)
		\end{itemize_3pt} 
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Typical Training Program}
	\begin{itemize_3pt}
	\item Content %\textcolor{}{}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Typical Training Program}
	\begin{itemize_3pt}
	\item Delivery %\textcolor{}{}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Impact on Businesses}
	\begin{itemize_3pt}
	\item First wave (Karlan and Valdivia, 2011, Field, et al., 2010; Bruhn \& Zia, 2013; Bulte et al., 2017; Anderson, Chandy, and Zia, 2018)
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Impact on Businesses}
	\begin{itemize_3pt}
	\item Econometric and implementation issues (McKenzie and Woodruff, 2014)
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Impact on Businesses}
	\begin{itemize_3pt}
	\item Recent evaluations (McKenzie, 2020)
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Targeted Training}
	\begin{itemize_3pt}
	\item Female entrepreneurs
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Targeted Training}
	\begin{itemize_3pt}
	\item Young entrepreneurs
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{On-site Consulting}
	\begin{itemize_3pt}
	\item Bloom, et al. (2013); Karlan et al (2015); Bruhn, Karlan \& Schoar (2019)
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

@@

\begin{frame}
\frametitle{Reliability of Self-reports}
	\begin{itemize_3pt}
	\item Self-reports of aggregate
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Reliability of Self-reports}
	\begin{itemize_3pt}
	\item Disaggregating quantities in self-reports
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Reliability of Self-report}
	\begin{itemize_3pt}
	\item Direct measures
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Sales vs. Profits}
	\begin{itemize_3pt}
	\item 
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Sales vs. Profits}
	\begin{itemize_3pt}
	\item 
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Heterogeneity of Impact}
	\begin{itemize_3pt}
	\item Heterogeneity of treatment effect poorly understood across different approaches
	\item Potential constraints are manifold, and likely context-dependent
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Education and literacy}
	\begin{itemize_3pt}
	\item Drexler, Fischer \& Schoar (2014)
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Rules of Thumb}
	\begin{itemize_3pt}
	\item Drexler, Fischer \& Schoar (2014)
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Rules of Thumb}
	\begin{itemize_3pt}
	\item 
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

%\bibliographystyle{econometrica}
%\bibliography{sampleBibFile}

>>>>

\documentclass[hideothersubsections, usenames,dvipsnames,10pt]{beamer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsmath}
\usepackage{mathpazo}
\usepackage{hyperref}
\usepackage{multimedia}
\usepackage{multicol}
\usepackage{epsfig}
\usepackage{curves}
\usepackage{epsfig}
\usepackage{epic}
\usepackage{curves}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{multicol}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{fix-cm}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{natbib}

@@

% Color scheme
\definecolor{cerulean}{rgb}{0.16, 0.32, 0.75}
\definecolor{bdf}{rgb}{0.19, 0.55, 0.91}
\definecolor{offwhite}{RGB}{255,253,243}
\definecolor{red}{RGB}{213,94,0}
%#09BADB #DB1A71

\usetheme[right]{Berkeley}
\setbeamercolor{background canvas}{bg=offwhite}
\setbeamercolor{palette primary}{bg=cerulean,fg=white}
\setbeamercolor{palette secondary}{bg=bdf,fg=white}
\setbeamercolor{frametitle}{fg=offwhite}
%\setbeamercolor{sidebar}{bg=cerulean}
%\newenvironment{transitionframe}{\setbeamercolor{background canvas}{bg=bdf}\begin{frame}}{\end{frame}}
%\setbeamercolor{title}{fg=black}
%\setbeamercolor{itemize item}{fg=blue}
%\setbeamercolor{itemize subitem}{fg=blue}
%\setbeamercolor{enumerate item}{fg=blue}
%\setbeamercolor{enumerate subitem}{fg=blue}
%\setbeamercolor{button}{bg=offwhite,fg=blue}

% Font
\setbeamerfont{section in sidebar}{size=\fontsize{5.3}{5}\selectfont}
\setbeamerfont{subsection in sidebar}{size=\fontsize{4.4}{5.5}\selectfont}
%\setbeamerfont{subsubsection in sidebar}{size=\fontsize{4}{7}\selectfont}
\setbeamerfont{title in sidebar}{}
\setbeamerfont{author in sidebar}{}
\setbeamercolor{section in sidebar}{bg=bdf,fg=offwhite}
\setbeamercolor{subsection in sidebar}{bg=bdf,fg=offwhite}

%\setbeamercolor{title}{bg=red!25!blue,fg=white}
%\setbeamercolor{fo} {bg=red!25!blue,fg=white}
%\setbeamercolor{sidebar}{bg=red!25!blue,fg=white}
%\setbeamercolor{author in sidebar}{fg=black!20!white}
%\setbeamercolor{title in sidebar}{fg=white}
%\setbeamercolor{normal text}{bg=white}
%\setbeamercolor{frametitle}{fg=white}
%\setbeamercolor{section in sidebar}{bg=black,fg=white}
%\setbeamercolor{subsection in sidebar}{bg=black,fg=white}
%\setbeamercolor{block title}{bg=red!25!blue,fg=white}
%\setbeamercolor{block body}{bg=blue!20!white,fg=black}
%\setbeamerfont{subsection in sidebar}{size=\tiny}
%\setbeamerfont{title in sidebar}{size=\scriptsize}
%\setbeamerfont{author in sidebar}{size=\tiny}
%\setbeamercovered{transparent}

@@

% Bibliography
%\renewcommand\bibliographytypesize{\small}
\renewcommand*{\bibfont}{\scriptsize}

@@

\begin{frame}
\frametitle{?}
	\begin{itemize_3pt}
	\item Bloom and van Reenen (2010, 2019): Business practices, motivation \citep{Bloom2010, Bloom2019}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Heterogeneity in Business Practices}
	\begin{itemize_3pt}
	\item Bloom and van Reenen (2010): Heterogeneity \citep{Bloom2010}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{}
	\begin{itemize_3pt}
	\item Bloom and van Reenen (2019): Correlation with productivity \citep{Bloom2019}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Business Practices in Small Firms}
	\begin{itemize_3pt}
	\item McKenzie and Woodruff (2009, 2017): Heterogeneity and predictiveness \citep{McKenzie2009, McKenzie2017}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Business Practices of Small Firms}
	\begin{itemize_3pt}
	\item McKenzie and Woodruff (2009, 2017): Example categories and practices \citep{McKenzie2009, McKenzie2017}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Best Practices for Small Firms}
	\begin{itemize_3pt}
	\item McKenzie and Woodruff (2017): Portable best practices \citep{McKenzie2017}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{History and Prevalence}
	\begin{itemize_3pt}
		\item At least \textcolor{bdf}{USD 1 billion per year} (to 4-5 million beneficiary entrepreneurs; \citet{McKenzie2020})
		\item Classical training programs \emph{precede} evidence that business practices vary and are predictive for productivity
		\vspace{0.1in}
		\item Examples:
		\begin{itemize_3pt}
			\item Start and Improve Your Business (ILO)
			\item Business Edge (IFC)
			\item EMPRETEC Entrepreneurship Training Workshop (UNCTAD)
		\end{itemize_3pt} 
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Typical Training Program}
	Content
	\begin{itemize_3pt}
	%\textcolor{}{}
	\item Training is delivered by 600 local certified trainers and by a pool of approximately 60 international master trainers. All trainers are also entrepreneurs.
	\item Empretec Training Workshops offer different levels of instruction that include:
	\item 6-day courses (48 hours); 32-hour (usually spread over 4 days) for micro-entrepreneurs with low levels of literacy; Interactive coaching based on real business challenges of participants.
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Typical Training Program}
	Delivery
	\begin{itemize_3pt}
	\item %\textcolor{}{}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Evidence on Impact}
	\begin{itemize_3pt}
	\item First wave (Karlan and Valdivia, 2011, Field, et al., 2010; Bruhn \& Zia, 2013; Bulte et al., 2017; Anderson, Chandy, and Zia, 2018)
					 \citep{Karlan2011} \citep{Field2010} \citep{Bruhn2013} \citep{Bulte2017} \citep{Anderson2018}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Evidence on Impact}
	\begin{itemize_3pt}
	\item Econometric and implementation issues \citep{McKenzie2014}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Evidence on Impact}
	\begin{itemize_3pt}
	\item Recent evaluations (McKenzie, 2020) \citep{McKenzie2020}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Targeted Training}
	Female entrepreneurs
	\begin{itemize_3pt}
		\item Example: Gender and Enterprise Together \citep[GET Ahead, ILO;][]{Bulte2016,McKenziePuerto2020}
		\item ?
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Targeted Training}
	Young entrepreneurs
	\begin{itemize_3pt}
		\item Entrepreneurship programs in school and university
		\item Example: University final year course in Tunisia \citep{Alaref2020}
		\item ?
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Specific Domains}
	\begin{itemize_3pt}
	\item \citep{Anderson2018}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Specific Domain}
	\begin{itemize_3pt}
	\item \citep{Anderson2018}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{On-site Consulting}
	\begin{itemize_3pt}
	\item Bloom, et al. (2013); Karlan et al. (2015); Bruhn, Karlan, and Schoar (2019)
	\item Large firms: \citep{Bloom2013}; SMEs: \citep{Bruhn2018}
	\item \citep{Karlan2015} \citep{Bruhn2019}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Multimedia delivery}
	TV shows
	\begin{itemize_3pt}
	\item Examples: Ruka Juu in Tanzania \citep{Bjorvatn2020} and El Mashroua in Egypt \citep{Barsoum2018}
	\item ?
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Multimedia delivery}
	TV shows
	\begin{itemize_3pt}
	\item Examples: Ruka Juu in Tanzania \citep{Bjorvatn2020} and El Mashroua in Egypt \citep{Barsoum2018}
	\item ?
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Multimedia delivery}
	Text messages
	\begin{itemize_3pt}
	\item \citep{Cole2019} \citep{Acimovic2020}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

% -----------------------

@@

\begin{frame}
\frametitle{Reliability of Self-reports}
	\begin{itemize_3pt}
	\item Self-reports of aggregate \citep{deMel2009}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Reliability of Self-reports}
	\begin{itemize_3pt}
	\item Disaggregating quantities in self-reports \citep{deMel2009}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Reliability of Self-report}
	\begin{itemize_3pt}
	\item Direct measures \citep{deMel2009}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Sales vs. Profits}
	\begin{itemize_3pt}
	\item  \citep{deMel2009}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Sales vs. Profits}
	\begin{itemize_3pt}
	\item \citep{deMel2009}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Heterogeneity of Impact}
	\begin{itemize_3pt}
	\item Heterogeneity of treatment effects poorly understood across different approaches
	\item Potential constraints are manifold, and likely context-dependent
	\item Some already mentioned in passing:
	\begin{itemize_3pt}
		\item Credit constraints \citep[see, e.g.,][]{} McKenzie cash paper
		\item Gender norms and constraints
		\item Age-related network and knowledge/skill constraints
	\end{itemize_3pt} 
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Education and literacy}
	\begin{itemize_3pt}
	\item Drexler, Fischer \& Schoar (2014) \citep{Drexler2014}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Rules of Thumb}
	\begin{itemize_3pt}
	\item Drexler, Fischer \& Schoar (2014) \citep{Drexler2014}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Rules of Thumb}
	\begin{itemize_3pt}
	\item \citep{Arraiz2019} \citep{Cole2019}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

%

\begin{frame}
\frametitle{Entrepreneurial mindset}
	\begin{itemize_3pt}
	\item \citep{Campos2017}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Entrepreneurial mindset}
	\begin{itemize_3pt}
	\item \citep{Alibhai2019} \citep{Ubfal2019}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

%\addtocontents{toc}{\protect\setcounter{tocdepth}{0}}

\subsection{References}
\begin{frame}[allowframebreaks]
\frametitle{References}

\bibliographystyle{econometrica}
\bibliography{SME_library}
\end{frame}
